An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-09-30 nips_2016.tex
Updated Figure 3 with accompanying discussion, added table for later usage

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{GaussianMixtureResult/minibatch_size_gaussian.png}
    \caption{
    Histograms of minibatch sizes for the three methods used in
    Section~\ref{ssec:gaussians}. {\color{blue} Daniel: The y-axis should
    probably just be ``Counts'' not ``Total Counts.'' Also, was this run with
    the \texttt{plt.tight\_layout()} command? The y-axis text for the second and
    third subplots almost overlap with the graphs to their left. Finally, I am
    still thinking about whether the y-axis should be on a log scale. I think
    the log scale is appropriate for the x-axis, it's a question of whether we
    should also apply it for the y-axis.}
    }
    \label{fig:gauss_mix_2}
\end{figure}

%% \begin{figure}[t]
%% 	\centering
%% 	\includegraphics[width=\linewidth]{GaussianMixtureResult/first_second_part_gaussian.png}
%% 	\caption{
%%     Value of first and second part of equation (9)
%%     in~\cite{icml2014c1_bardenet14} with respect to actual minibatch size.
%%     {\color{blue} Daniel: probably debatable on whether we should include this.
%%     Let's talk it over.}
%%     }
%% 	\label{fig:gauss_bardenet}
%% \end{figure}

@@

The results for each model are shown in table 2...

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{minibatch_size_gaussian.png}
    \caption{
    Histograms of minibatch sizes for the three methods used in
    Section~\ref{ssec:gaussians}. Note the log-log scale, to facilitate
    comparisons across methods; in particular, the axes have the same
    range.
    }
    \label{fig:gauss_mix_2}
\end{figure}

@@

The results for each model are shown in Table~\ref{tab:poissons} ...
{\color{blue} Daniel: IN PROGRESS}

\begin{table}[t]
    \caption{{\color{blue} Daniel: TODO Poisson Probabilities}}
    \label{tab:poissons}
    \centering
    \begin{tabular}{l l l l}
    \toprule
    Model & Ours & Korattikara 2014 & Bardenet 2014 \\
    \midrule
    Poission Value & TODO & TODO & TODO \\
    \bottomrule
    \end{tabular}
\end{table}
